Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by laser speckle contrast imaging

### 2021-07-14 article.tex
Initial revision for submission to Journal of Neuroscience Methods
- Focus more on acute dynamics of anesthesia rather than before/after measurements
- Swapped back to original MESI equation (Parthasarathy, 2008)
- Added analysis of isoflurane dynamics (flow rise time)
- Transitioned to Elsevier style

\documentclass[12pt]{spieman}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage[version=4]{mhchem}

@@

% ---------------------------------------------------------------------------------------
% BEGIN TITLE AND AUTHORS
% ---------------------------------------------------------------------------------------
\title{Visualizing anesthesia-induced vasodilation of cerebral vasculature using multi-exposure speckle imaging}

\author[a]{Colin T. Sullender}
\author[a]{Lisa M. Richards}
\author[b]{Fei He}
\author[b,c]{Lan Luan}
\author[a,*]{Andrew K. Dunn}
\affil[a]{Department of Biomedical Engineering, University of Texas at Austin, 107 W. Dean Keeton Street Stop C0800, Austin, Texas, 78712, United States}
\affil[b]{Department of Electrical and Computer Engineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}
\affil[c]{Department of Bioengineering, Rice University, 6100 Main Street, Houston, TX, 77005, United States}

% ----------------------------------------------------------------------------------------
% BEGIN DOCUMENT
% ----------------------------------------------------------------------------------------
\renewcommand{\cftdotsep}{\cftnodots}
\cftpagenumbersoff{figure}
\cftpagenumbersoff{table} 
\begin{document} 
\maketitle

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}
Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology. In this paper, we characterize the impact of isoflurane on cerebral blood flow (CBF) during the induction of general anesthesia in awake mice using multi-exposure speckle imaging (MESI). We highlight the large anatomical changes caused by the vasodilatory inhalant with wide-field imagery and quantify the cortical hemodynamics with MESI across multiple subjects and imaging sessions. Compared to the awake state, we measured, on average, an 18\% increase in surface vessel diameter accompanied by a 135\% increase in vascular flux and 92\% increase in parenchyma perfusion. These large alterations to the cortical vasculature and CBF are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.
\end{abstract}

% Include a list of up to six keywords after the abstract
\keywords{multi-exposure speckle imaging, laser speckle contrast imaging, awake imaging, anesthesia, isoflurane, cerebral blood flow}

% Include email contact information for corresponding author
{\noindent \footnotesize\textbf{*}Andrew K. Dunn, \linkable{adunn@utexas.edu}}

\begin{spacing}{2}   % use double spacing for rest of manuscript

% ----------------------------------------------------------------------------------------
% BEGIN INTRODUCTION SECTION
% ----------------------------------------------------------------------------------------
\section{Introduction}
\label{sect:introduction}

The use of general anesthesia during neuroimaging is ubiquitous across many animal models despite systemic effects on neurophysiological state and cardiovascular function \cite{Slupe:2018ea}. Volatile inhalation anesthetics, such as the halogenated ether isoflurane \cite{Eger:1981ia}, are commonly utilized to immobilize animals during imaging while allowing for fine control over the depth of anesthesia and consciousness. However, isoflurane has been shown to reduce neuronal activity \cite{Aksenov:2015ea} and functional connectivity \cite{Xie:2019de}, suppress the magnitude and speed of neurovascular coupling \cite{Masamoto:2012bj,Takuwa:2012ee,Pisauro:2013cx}, and induce significant vasodilation \cite{Koenig:1994rn,Strebel:1995uh,Iida:1998th}. Isoflurane also conveys potential neuroprotective effects that reduce and delay the severity of cerebral ischemia \cite{Kitano:2007ia,Kawaguchi:2000id,Sakai:2007wc,Li:2013ip,Lu:2017bo}. These effects can mask the benefits of prospective neuroprotective therapeutics or interventions and confound the outcomes of long-term studies \cite{Kapinya:2002ua,Seto:2014ga}. For these reasons and more \cite{Gao:2017tw}, there is a growing effort within the neuroscience community to transition to un-anesthetized awake animal models in order to more accurately interpret neurophysiological and behavioral experiments and more readily translate findings to awake human physiology.

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response to local neural activity via neurovascular coupling \cite{Sicard:2003dj,Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) of photothrombotic stroke observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. To our knowledge, no prior studies have directly monitored the induction of general anesthesia and its acute effects upon the cerebral vasculature.

In this paper, we present multi-exposure speckle imaging (MESI) of cerebral blood flow in awake mice during the induction of general anesthesia with isoflurane. The MESI technique \cite{Parthasarathy:2008el} provides a more robust estimate of large changes in flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo} and enables the chronic tracking of CBF \cite{Kazmi:2013hp}. We highlight the large anatomical and physiological changes to cortical hemodynamics in response to isoflurane with wide-field imagery across multiple imaging sessions and animals. Because the anesthetized state is representative of an abnormal physiology, we argue that awake animal models should be utilized whenever possible for neuroscience studies.

% ----------------------------------------------------------------------------------------
% BEGIN METHODS SECTION
% ----------------------------------------------------------------------------------------
\section{Methods}
\label{sect:methods}

\subsection{Multi-Exposure Speckle Imaging (MESI)}
A schematic of the imaging system is presented in Fig.~\ref{fig:system_image}a. MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle. The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) with $2\times$ magnification and cropped to a field-of-view of 3.6 $\times$ 3.0 mm. Camera exposures were temporally synchronized with the modulated laser pulses. Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages \cite{Sullender:2018ff}.

The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7$\times$7-pixel sliding window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
%
% Equation 1 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K(T,\tau_c) =
        \left(
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \beta(1 - \rho)^2 +
        \nu_{noise}
        \right)^{1/2}
\end{equation}

\noindent where $T$ is the camera exposure time, $x = T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu_{noise}$ represents exposure-independent instrument noise and nonergodic variances. Eq.~(\ref{eq:mesi}) was fitted with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:2005} using a custom program written in C.

@@

Cranial window implanted mice ($n = 3$, Subjects 2-4) were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined prior to continuous imaging by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ min), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane to the subject. After two minutes of exposure ($t = 12$ min), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ min, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

An additional animal (Subject 1) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics. Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery. The timing of the anesthesia induction was identical to the protocol described above with the awake and anesthetized states defined at $t = 0$ and $t = 120$ minutes, respectively. The four repeated imaging sessions for this subject were spaced at least one week apart to minimize any complications from extended anesthesia exposure.

@@

While head fixation can greatly minimize locomotion-associated brain movement \cite{Dombeck:2007gr}, it does not completely eliminate motion artifacts. The induction of general anesthesia also causes a major change in posture that can result in lateral displacements of the brain relative to the skull. In order to account for these shifts, the open source image registration toolbox \texttt{Elastix} \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the awake baseline imagery prior to fitting Eq.~(\ref{eq:mesi}). The resulting aligned MESI $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second (8$\times$ speed). $ICT$ timecourses spanning the entire imaging session were also extracted from the fitted data from both vascular and parenchymal regions of interest.

In order to calculate the vascular flux, the diameter of the vessels ($d_{vessel}$) were estimated using the 5 ms exposure speckle contrast frames. Cross-sectional profiles were extracted from each vessel at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution. Because LSCI is most sensitive to moving scatterers, i.e. erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel. The vascular flux was then computed by scaling the MESI $ICT$ by $d_{vessel}$ at each timepoint \cite{Kazmi:2015du}. Relative changes in vascular flux and perfusion were calculated using the average of the entire awake state as the baseline.

% ----------------------------------------------------------------------------------------
% BEGIN RESULTS SECTION
% ----------------------------------------------------------------------------------------
\section{Results}
\label{sect:results}

The systematic changes caused by general anesthesia with isoflurane in Subject 1 are shown in Fig.~\ref{fig:system_image}b and Video 1, which highlights the transition from the awake to the anesthetized state. The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane \cite{Masamoto:2012bj}. Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased. These large alterations to the vasculature complicated rigid image registration and precluded the generation of relative flow change imagery.

% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure1.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:system_image}
        (a) MESI system schematic with 2$\times$ magnification: A (Standard Iris, ID15, Thorlabs, Inc.), M ({{\O}}1$''$ Broadband Dielectric Mirror, BB1-E02, Thorlabs, Inc.), L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.). (b) Single exposure LSCI (5 ms) and MESI inverse correlation time during awake and anesthetized states in Subject 1 (Scale bar = 1 mm) (Video 1, MPEG4, 35.8 MB).
    }
\end{figure}

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:acute}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session in Subject 1. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:acute}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:acute}b. The width of the two vessels remained steady throughout the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the relative changes in vascular flux and parenchymal tissue perfusion (Fig.~\ref{fig:acute}c). The vascular flux in R1 and R2 increased by 267\% and 175\%, respectively, while the tissue perfusion in R3 grew by 161\%. The large deviation shortly after $t = 80$ minutes was caused by the subject briefly experiencing breathing difficulties that required the anesthesia to be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size. Repeated measurements in the subject (Figs.~\ref{fig:acute}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to the isoflurane anesthesia.

% Figure 2 - Extended Awake to Anesthetized Measurements
\begin{figure}
    \begin{center}
        \begin{tabular}{c}
            \includegraphics[width=6.25in]{Figure2.pdf}
        \end{tabular}
    \end{center}
    \caption {
        \label{fig:acute}
        (a) Awake speckle contrast image (5 ms) from Subject 1 overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis (Scale bar = 500 $\mu$m). Dashed lines indicate the cross-sectional profiles used to calculate vessel width. Timecourses of (b) vessel diameter and (c) relative change in blood flow within the regions over the extended two-hour imaging session. The vertical dashed line indicates the beginning of anesthesia induction. The relative vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline. Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in Subject 1 across four imaging sessions (mean $\pm$ sd). Statistics computed across the 50 MESI frames acquired in each state.
    }
\end{figure}

The repeatability of these measurements were further demonstrated across Subjects 2-4 as shown in Fig.~\ref{fig:summary}. Two vascular regions (R1 and R2) and two parenchyma regions (R3 and R4) were examined in each animal during the awake and anesthetized states across three separate imaging sessions lasting 30 minutes each. Similar to the results seen in Fig.~\ref{fig:acute}, the vasodilatory effects of isoflurane anesthesia induced large changes in the cortical hemodynamics. On average, vessel width increased by 13\% and vascular flux increased by over 80\%, with the exception of R2 from Subject 2, which only experienced minimal vasodilation (+1.4\%) and therefore a smaller increase in vascular flux (+63\%). The perfusion of parenchymal regions increased on average by 80\% across all three subjects.

>>>>

\documentclass[review]{elsarticle}

\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{tocloft}
\usepackage[version=4]{mhchem}

@@

% Structured abstract section formatting
\newcommand{\abstractsection}[1]{
  \par\addvspace{.5\baselineskip}
  \noindent\textbf{#1: }\ignorespaces
}

% ----------------------------------------------------------------------------------------
% BEGIN DOCUMENT
% ----------------------------------------------------------------------------------------
\begin{document}

\begin{frontmatter}

\journal{Journal of Neuroscience Methods}

\title{Dynamics of isoflurane-induced vasodilation and blood flow of cerebral vasculature revealed by laser speckle contrast imaging}

% Authors
\author[a]{Colin T. Sullender}

\author[a]{Lisa M. Richards}

\author[b]{Fei He}

\author[b,c]{Lan Luan}

\author[a]{Andrew K. Dunn\corref{corr_auth}}
\ead{adunn@utexas.edu}
\cortext[corr_auth]{Corresponding Author}

% Affiliations
\affiliation[a]{
    organization={Department of Biomedical Engineering, University of Texas at Austin},
    addressline={107 W. Dean Keeton Street Stop C0800},
    city={Austin, TX},
    postcode={78712},
    country={United States}
}

\affiliation[b]{
    organization={Department of Electrical and Computer Engineering, Rice University},
    addressline={6100 Main Street},
    city={Houston, TX},
    postcode={77005},
    country={United States}
}

\affiliation[c]{
    organization={Department of Bioengineering, Rice University},
    addressline={6100 Main Street},
    city={Houston, TX},
    postcode={77005},
    country={United States}
}

% ----------------------------------------------------------------------------------------
% BEGIN ABSTRACT
% ----------------------------------------------------------------------------------------
\begin{abstract}

\abstractsection{Background}
Anesthetized animal models are used extensively during neurophysiological and behavioral studies despite systemic effects from anesthesia that undermine both accurate interpretation and translation to awake human physiology. The majority of work examining the impact of anesthesia on cerebral blood flow (CBF) has been limited to before and after measurements with limited spatial resolution.

\abstractsection{New Method}
We used multi-exposure speckle imaging (MESI), an advanced form of laser speckle contrast imaging (LSCI), to characterize the dynamics of isoflurane anesthesia induction on cerebral vasculature and blood flow in the mouse brain.

\abstractsection{Results}
The large anatomical changes caused by isoflurane are depicted with wide-field imagery and video highlighting the induction of anesthesia. Compared to the awake state, we measured, on average, a 14.1\% increase in surface vessel diameter accompanied by a 96.0\% increase in vascular flux and 84.7\% increase in parenchyma tissue perfusion. We also examined the dynamics of anesthesia induction and found that blood flow increased faster in arterioles than in venules or parenchyma regions.

\abstractsection{Comparison with Existing Methods}
MESI offers robust hemodynamic measurements across large fields-of-view and high temporal resolutions sufficient for continuous visualization of cerebrovascular events.

\abstractsection{Conclusion}
The large alterations caused by isoflurane anesthesia to the cortical vasculature and CBF are readily characterized using MESI. These changes are unrepresentative of normal physiology and provide further evidence that neuroscience experiments would benefit from transitioning to un-anesthetized awake animal models.

\end{abstract}

% Include a list of up to six keywords after the abstract
\begin{keyword}
    laser speckle contrast imaging \sep
    multi-exposure speckle imaging \sep
    awake imaging \sep
    anesthesia \sep
    hemodynamics \sep
    cerebral blood flow
\end{keyword}

\end{frontmatter}

% ----------------------------------------------------------------------------------------
% BEGIN INTRODUCTION SECTION
% ----------------------------------------------------------------------------------------
\section{Introduction}

The use of general anesthesia during neuroimaging is ubiquitous across many animal models despite systemic effects on neurophysiological state and cardiovascular function \cite{Slupe:2018ea}. Volatile inhalation anesthetics, such as the halogenated ether isoflurane \cite{Eger:1981ia}, are commonly utilized to immobilize animals during imaging while allowing for fine control over the depth of anesthesia and consciousness. However, isoflurane has been shown to reduce neuronal activity \cite{Aksenov:2015ea} and functional connectivity \cite{Xie:2019de}, suppress the magnitude and speed of neurovascular coupling \cite{Masamoto:2012bj,Takuwa:2012ee,Pisauro:2013cx}, and induce significant vasodilation \cite{Koenig:1994rn,Iida:1998th}. Isoflurane also conveys potential neuroprotective effects that reduce and delay the severity of cerebral ischemia \cite{Kitano:2007ia,Kawaguchi:2000id,Sakai:2007wc,Li:2013ip,Lu:2017bo}. These effects can mask the benefits of prospective neuroprotective therapeutics or interventions and confound the outcomes of long-term studies \cite{Kapinya:2002ua,Seto:2014ga}. For these reasons and more \cite{Gao:2017tw}, there is a growing effort within the neuroscience community to transition to un-anesthetized awake animal models in order to more accurately interpret neurophysiological and behavioral experiments and more readily translate findings to awake human physiology.

There have been numerous imaging modalities used to examine the effects of isoflurane on cerebral hemodynamics. Functional magnetic resonance imaging (fMRI), laser Doppler flowmetry, and intrinsic signal optical imaging have all established that isoflurane increases basal cerebral blood flow (CBF) while attenuating and delaying the hemodynamic response to local neural activity via neurovascular coupling \cite{Desai:2011mb,Aksenov:2015ea,Takuwa:2012ee,Pisauro:2013cx}. Two-photon phosphorescence lifetime microscopy showed that tissue oxygenation is twice as high under isoflurane anesthesia compared to the awake state and exhibited large layer-specific differences within the cortical vasculature \cite{Lyons:2016bd}. Calcium signal imaging following ischemic stroke found that the magnitude of spreading depolarizations were significantly smaller in awake mice \cite{Balbi:2017cj} while laser speckle contrast imaging (LSCI) of photothrombotic stroke observed larger infarct sizes in awake rats compared to their isoflurane-anesthetized counterparts \cite{Lu:2017bo}. To our knowledge, no prior studies have directly imaged the induction of general anesthesia and its acute effects upon the cerebral vasculature.

In this paper, we present multi-exposure speckle imaging (MESI) of cerebral blood flow in awake mice during the induction of general anesthesia with isoflurane. The MESI technique \cite{Parthasarathy:2008el} provides a more robust estimate of large changes in flow compared to traditional single-exposure LSCI \cite{Parthasarathy:2010vo} and enables the chronic tracking of CBF \cite{Kazmi:2013hp}. We examine the dynamics of the large anatomical and physiological changes to cortical vasculature in response to isoflurane with wide-field imagery across multiple imaging sessions and animals. Because the anesthetized state is representative of an abnormal physiology, we argue that awake animal models should be utilized whenever possible for neuroscience studies.

% ----------------------------------------------------------------------------------------
% BEGIN METHODS SECTION
% ----------------------------------------------------------------------------------------
\section{Materials and Methods}

\subsection{Multi-Exposure Speckle Imaging (MESI)}
A schematic of the imaging system is presented in Fig.~\ref{fig:system}a. MESI was performed using a 685 nm laser diode (50 mW, HL6750MG, Thorlabs, Inc.) intensity modulated with an acousto-optic modulator (AOM, 3100-125, Gooch \& Housego, Ltd.) and relayed to illuminate the craniotomy at an oblique angle. The scattered light was imaged by a CMOS camera (acA1920-155um, Basler AG) with $2\times$ magnification and cropped to a field-of-view of 3.6 $\times$ 3.0 mm. Camera exposures were temporally synchronized with the modulated laser pulses. Fifteen camera exposures ranging between 50 $\mu$s and 80 ms \cite{Parthasarathy:2008el,Atchia:2013ep,Kazmi:2013hp} were recorded for each complete MESI frame in order to broadly sample the speckle dynamics of the specimen \cite{Kazmi:2014go}, resulting in an effective acquisition rate of $\sim$2.5 MESI frames-per-second. The total amount of light used to capture each exposure was held constant with the AOM in order to minimize the effects of shot noise \cite{Parthasarathy:2008el}. The acquisition was controlled using custom software written in C++ along with a multifunction I/O device (USB-6363, National Instruments Corp.) for the generation of camera exposure trigger signals and AOM modulation voltages \cite{Sullender:2018ff}.

The 15 raw intensity images were converted to speckle contrast images ($K = \sigma_{s} / {\langle{I}\rangle}$) with a 7$\times$7-pixel sliding window and used to calculate an estimate of the speckle correlation time ($\tau_c$) at each pixel with the multi-exposure speckle visibility expression \cite{Parthasarathy:2008el}:
%
% Equation 1 - MESI Equation
\begin{equation}
    \label{eq:mesi}
    K(T,\tau_c) =
        \left(
        \beta\rho^2\frac{e^{-2x} - 1 + 2x}{2x^2} +
        4\beta\rho(1 - \rho)\frac{e^{-x} - 1 + x}{x^2} +
        \nu_{noise}
        \right)^{1/2}
\end{equation}

\noindent where $T$ is the camera exposure time, $x = T/\tau_c$, $\rho$ is the fraction of light that is dynamically scattered, $\beta$ is a normalization factor that accounts for speckle sampling, and $\nu_{noise}$ represents exposure-independent instrument noise and nonergodic variances. Eq.~(\ref{eq:mesi}) was fitted with the Levenberg-Marquardt nonlinear least squares algorithm \cite{Lourakis:J2fCMU5i} using a custom program written in C.

@@

Cranial window implanted mice were head constrained on the awake imaging system and allowed to acclimate for 5-10 minutes. The awake hemodynamic baseline was then defined prior to continuous imaging by acquiring 50 MESI frames, averaging the speckle contrast across each exposure time, and computing the corresponding $ICT$ frame using Eq.~(\ref{eq:mesi}). A custom 3D-printed inhalation nose-cone connected to the anesthesia vaporizer and scavenger was then placed several millimeters away from the subject and used to administer medical air (0.5 L/min) with no isoflurane (0\%). Continuous MESI was initiated ($t = 0$) and used to monitor the awake subject for 10 minutes before increasing isoflurane to 2.0\% to induce anesthesia. After one minute of exposure ($t = 11$ minutes), the nose-cone was fully positioned over the subject to ensure targeted delivery of isoflurane to the subject. After two minutes of exposure ($t = 12$ minutes), a feedback heating pad (55-7030, Harvard Apparatus, Inc.) was placed beneath the subject to maintain a 37 $^\circ$C body temperature. The now anesthetized subject was continuously monitored with MESI until $t = 30$ minutes, at which point the anesthetized hemodynamic state was defined by acquiring and averaging an additional 50 MESI frames. The subject was then removed from the imaging system and allowed to recover from anesthesia on a heating pad before being transferred back into its cage. Each subject underwent three imaging sessions with at least one full day of recovery between each session.

One animal (Subject 1) underwent an extended routine where the awake and anesthetized states were each imaged for one hour in order to capture the longer-term hemodynamics. Because of the volume of data being recorded, the acquisition was briefly paused prior to the induction of anesthesia to offload data from the solid-state drive used for writing data, which resulted in a short period of missing imagery. The timing of the anesthesia induction was identical to the protocol described above with the awake and anesthetized states defined at $t = 0$ and $t = 120$ minutes, respectively. The four repeated imaging sessions for this subject were spaced at least one week apart to minimize any complications from extended anesthesia exposure.

@@

All data processing was performed using MATLAB (R2021a, MathWorks, Inc.). While head fixation can greatly minimize locomotion-associated brain movement \cite{Dombeck:2007gr}, it does not completely eliminate motion artifacts. The induction of general anesthesia also causes major changes in posture that can result in lateral displacements of the brain relative to the skull. In order to account for these shifts, the open source image registration toolbox \texttt{Elastix} \cite{Klein:2010gr} was used to rigidly align all speckle contrast frames to the baseline awake imagery prior to fitting Eq.~(\ref{eq:mesi}). The resulting aligned MESI $ICT$ frames were then smoothed temporally with a central moving average filter ($k=5$) and rendered to video at 20 frames-per-second (8$\times$ speed). $ICT$ timecourses spanning the entire imaging session were then extracted from the aligned data from both vascular and parenchymal regions of interest (ROIs).

\subsubsection{Calculating Vascular Flux}
In order to calculate the vascular flux \cite{Kazmi:2015du}, the diameter of vessels ($d_{vessel}$) were estimated using the 5 ms exposure speckle contrast frames. Cross-sectional profiles were extracted across each vessel of interest at every timepoint and fitted to a Gaussian function in order to calculate the full-width at half-maximum (FWHM) of the distribution over time. Because LSCI is most sensitive to moving scatterers, i.e. erythrocytes, this method of estimating $d_{vessel}$ is a measure of the inner diameter of the vessel. The vascular flux was then computed by scaling the MESI $ICT$ by $d_{vessel}$ at each timepoint (arbitrary units). The percent change in vessel diameter and vascular flux were calculated using the average of the entire awake state for the baseline.

\subsubsection{Calculating Blood Flow Rise Time}
To examine the dynamics of isoflurane-induced flow changes, the rise time in measured blood flow was calculated. Rise time was defined as the time elapsed following the start of anesthesia for $ICT$ values to increase by 50\% relative to the awake baseline. A spatially-resolved blood flow rise time map was generated for Subject 1 by performing this calculation pixel-wise across the entire field-of-view. Analogous rise time calculations were performed on the vascular flux and parenchymal tissue perfusion metrics across all subjects and imaging sessions using the previously extracted ROI timecourses.

\subsubsection{Statistical Analysis}
All statistical analyses were performed using MATLAB (R2021a, MathWorks, Inc.). The differences between arteriole, venule, and parenchymal measurements were evaluated with one-way ANOVAs using the Bonferroni method for multiple comparisons. $p \leq 0.05$ was considered statistically significant.

% ----------------------------------------------------------------------------------------
% BEGIN RESULTS SECTION
% ----------------------------------------------------------------------------------------
\section{Results}

The systematic changes caused by general anesthesia with isoflurane in Subject 1 are shown in Fig.~\ref{fig:system}b and Video 1, which highlights the transition from the awake to the anesthetized state. The visible decrease in speckle contrast and corresponding increase in MESI $ICT$ are representative of an increase in CBF caused by the vasodilatory effects of isoflurane. Dilation is seen across much of the surface vasculature, in particular the large central vein and numerous smaller vessels that have become more prominent in the anesthetized imagery as blood flow increased. These large alterations to the vasculature complicated rigid image registration and precluded the generation of relative flow change imagery.

% Figure 1 - System Schematic + Awake vs. Anesthetized Imagery
\begin{figure}
    \includegraphics[width=\textwidth]{Figure1.pdf}
    \caption {
        (a) MESI system schematic with 2$\times$ magnification: A (Standard Iris, ID15, Thorlabs, Inc.), M ({{\O}}1$"$ Broadband Dielectric Mirror, BB1-E02, Thorlabs, Inc.), L1 ($f =$ 50 mm, Steinheil Triplet Achromatic, 67-422, Edmund Optics, Inc.), F (685 $\pm$ 20 nm bandpass filter, S685/40m, Chroma Technology Corp.), and L2 ($f = 100$ mm, Achromatic Doublet, AC254-100-A, Thorlabs, Inc.). (b) Single exposure LSCI (5 ms) and MESI inverse correlation time ($ICT$) during awake and anesthetized states in Subject 1 (Scale bar = 1 mm) (Video 1, MPEG-4, 35.8 MB).
    }
    \label{fig:system}
\end{figure}

The temporal dynamics of the awake-to-anesthetized transition can be seen in Fig.~\ref{fig:timecourse}, where the change in blood flow within two veins (R1 and R2) and one parenchyma region (R3) were analyzed during the extended two-hour imaging session in Subject 1. The cross sections used to estimate $d_{vessel}$ are depicted in Fig.~\ref{fig:timecourse}a with the resulting changes in vessel diameter shown in Fig.~\ref{fig:timecourse}b. The width of the two vessels remained steady throughout the entirety of the awake measurements but increased under anesthesia, with the larger vessel (R1) growing by over 50\% after an hour of exposure. This vasodilation was also accompanied by an increase in blood flow as measured by the percent change in vascular flux and parenchymal tissue perfusion as shown in Fig.~\ref{fig:timecourse}c. The vascular flux in R1 and R2 increased by 270\% and 144\%, respectively, while the tissue perfusion in R3 grew by 141\%. The large deviation shortly after $t = 80$ minutes was caused by the subject briefly experiencing breathing difficulties that required the anesthesia be reduced to 1.5\% isoflurane for several minutes. The breathing abnormality and change in anesthesia dosage had no apparent effects on the vessel size. Repeated measurements in the subject (Figs.~\ref{fig:timecourse}d-f) illustrate the stability of day-to-day MESI estimates of blood flow as well as the consistency of the hemodynamic response to isoflurane anesthesia.

% Figure 2 - Extended Awake to Anesthetized Measurements
\begin{figure}
    \includegraphics[width=\textwidth]{Figure2.pdf}
    \caption {
        (a) Awake speckle contrast image (5 ms) from Subject 1 overlaid with vascular (R1 and R2) and parenchyma (R3) regions used during flow analysis (Scale bar = 500 $\mu$m). Dashed lines indicate the cross-sectional profiles used to calculate vessel width. Timecourses of (b) vessel diameter and (c) percent change in blood flow within the regions over the extended two-hour imaging session. The vertical dashed line indicates the beginning of anesthesia induction. The percent change in vascular flux and tissue perfusion in (c) were computed using the average of the entire awake state for the baseline. Repeated measurements of (d) vessel diameter, (e) vascular flux, and (f) parenchyma tissue perfusion during awake and anesthetized states in Subject 1 across four imaging sessions (mean $\pm$ sd). Statistics computed across the 50 MESI frames acquired in each state.
    }
    \label{fig:timecourse}
\end{figure}

The percent changes in vessel diameter and blood flow between the awake and anesthetized states were aggregated across all subjects and imaging sessions as shown in Fig.~\ref{fig:aggregated}. The anesthetized measurements for Subject 1, which underwent the extending imaging sessions, were taken at $t \approx 80$ minutes to match the timing of the other subjects (20 minutes after the start of anesthesia). A total of 108 measurements were included in the analysis (33 arteriole, 29 venule, 46 parenchyma). Similar to the results seen in Fig.~\ref{fig:timecourse}, the vasodilatory effects of isoflurane induced large changes in the cortical hemodynamics. On average, vessel width increased by 14.1\%, with arterioles increasing by 15.0\% and venules increasing by 13.0\% (Fig.~\ref{fig:aggregated}a). There was no significant difference in the percent change in width between arterioles and venules ($p = 0.61$). Vascular flux increased, on average, by 96.0\%, with arterioles increasing by 81.7\% and venules increasing by 112.2\% (Fig.~\ref{fig:aggregated}b). Parenchymal tissue perfusion increased by 84.7\%. While the ANOVA was significant ($p = 0.041$), the multiple pairwise comparisons between arterioles, venules, and parenchyma were all non-significant ($p > 0.05$).
